### 2017-02-08 CO750-ApproximationAlgorithmsTopics/assignments/assignment_01.tex
q5 a1

\paragraph{An Approximation Algorithm for $IP$}

@@

>>>>

\paragraph{Integrality Gap for $IP$}

@@

We claim that the solution $\bar{x}$ returned by $\cB$ is feasible for $IP$. To see this, observe that completing $T$ to the graph $G$ does not remove any edges across any cut set $S$, hence the bound $\sum_{e \in \delta(S)} \bar{x}_e \geq f(S)$ still holds, since additional edges contribute non-negative amounts to $\sum_{e \in \delta(S)}$. This implies that $\bar{x}$ is feasible for $IP$ on $G$.
Now we analyze the cost. We see that
$$\sum_{u,v \in V} d(u,v) \bar{x}_{uv} \leq \sum_{u,v \in V} d^T(u,v) \bar{x}_{uv}$$
from Theorem \ref{th:metric-tree}.
